QSO decomposition

### 2018-12-03 manuscript/manuscript.tex
fit result before re-fit the other QSO using CID597 and CID1281's PSF

Our final sample is composed of 36  AGNs; 32 of them are new systems \textcolor{red}{\bf (32+4?, the information of these four sample?)}. To compare with the samples in the literature, we adopt the samples from ... \textcolor{blue}{\bf The samples from H0licow7}
For the calibration with the local relation, we introduce the well-defined 19 local AGN measurements \citep{Ben++10, Peterson2004} which defines the zero-point. Table~\ref{tab:objlist} list all the AGN systems analyzed in this work.

@@

With the self-consistent cross-calibration, we estimate the \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}. For the system with both \halpha\ and \hbeta\ emission line information, we adopt the average \mbh\ value by these two. We summarized the inference of the \mbh\ together with the details on the emission line in Table~\ref{tab:result_mbh}.

@@

\section{discuss}
\label{sec:dis}
\subsection{Systematic error}
\subsection{Fitting mask for CID1174 and ECDFS-358}

@@

\begin{deluxetable*}{ccccccc}
\tablecolumns{7}
\tablewidth{0pt}
\tablecaption{Details of the weighting for the inference of CID1174. } 
\tablehead{ 
\colhead{PSF rank} &
\colhead{total $\chi ^2$} & 
\colhead{weights $w_i$} &
\colhead{host flux (counts)} &
\colhead{host flux ratio}&
\colhead{\Reff (arcsec)}&
\colhead{\sersic\ $n$}
 \\ 
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)} &
\colhead{(6)} &
\colhead{(7)} 
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
1 & 8646.711 & 1.000 & 99.102 & 41.9\% & 0\farcs{}298 & 1.932 \\
2 & 8816.947 & 0.849 & 76.740 & 33.0\% & 0\farcs{}365 & 1.102 \\
3 & 9304.841 & 0.530 & 128.618 & 54.7\% & 0\farcs{}231 & 2.780 \\
4 & 9652.575 & 0.379 & 187.498 & 79.0\% & 0\farcs{}116 & 6.175 \\
5 & 10018.324 & 0.267 & 75.061 & 32.3\%& 0\farcs{}365 & 1.226 \\
6 & 10087.456 & 0.249 & 79.835 & 34.3\% & 0\farcs{}358 & 1.195 \\
7 & 10457.811 & 0.174 & 108.580 & 46.4\% & 0\farcs{}262 & 2.190 \\
8 & 10721.421 & 0.135 & 63.994 & 27.8\% & 0\farcs{}406 & 0.720 \\
\hline\\
Weighted value & & & 103.534 $\pm$ 34.267 & 44.0\%$\pm$14.2\%& 0\farcs{}296$\pm$0\farcs{}079 & 2.173$\pm$1.500  \\
\enddata
\label{tab:weight_CID1174}
\tablecomments{
Column~1: The rank of the PSF from the library.
Column~2: Total $\chi ^2$ for the corresponding PSF.
Column~3: Weights for co-adding the inference.
Column~4-7: Fitted value for the host flux, host/total flux ratio, effective radius, and \sersic\ index.
For this sample, the inflation value $\alpha$ calculated by Eq.~\ref{eq:alpha} is 16.671.
}
\end{deluxetable*}

@@

\begin{deluxetable*}
{@{\extracolsep{4pt}}lcccccc}   % need for the gap between the clines.
\tablecolumns{7}
\tablewidth{0pt}
\tablecaption{The inference of the \mbh\ for the 32 systems.} 
\tablehead
{ 
\colhead{Target ID}&
  \multicolumn{3}{c}{using emission line \halpha}&
  \multicolumn{3}{c}{using emission line \hbeta} \\
  \cline{2-4}  \cline{5-7} \\
\colhead{}& 
\colhead{FWHM}& \colhead{$\log(\lambda \rm L _{H\alpha}$)}& \colhead{\mbh}&
\colhead{FWHM(5100)}& \colhead{$\log(\lambda \rm L _{\lambda5100})$}& \colhead{\mbh}\\
\colhead{}& 
\colhead{(\kms)}& \colhead{(${\rm erg~s^{-1}}$)}& 
\colhead{(M$_{\odot}$)}& \colhead{(\kms)}& 
\colhead{(${\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)}\\
\colhead{(1)}& 
\colhead{(2)}& \colhead{(3)}& 
\colhead{(4)}& \colhead{(5)}& 
\colhead{(6)}&\colhead{(7)}
}
\startdata 
CID1174 & 1906.3037 & 43.43237 & 7.807 & 5898.264 & 44.76243 & 8.818 \\
CID1281 & 1619.4891 & 43.23945 & 7.559 & ... & ... & ... \\
CID206 & 3333.5527 & 43.4776 & 8.317 & ... & ... & ... \\
CID216 & 2229.5232 & 42.84509 & 7.620 & ... & ... & ... \\
CID237 & 2112.3306 & 43.85546 & 8.129 & ... & ... & ... \\
CID255 & 1932.0933 & 43.9924 & 8.127 & 3709.241 & 45.37122 & 8.731 \\
CID3242 & 2543.2202 & 43.83323 & 8.278 & 3774.503 & 45.09891 & 8.605 \\
CID3570 & 1958.8551 & 43.16374 & 7.683 & ... & ... & ... \\
CID452 & 3457.8801 & 42.92298 & 8.044 & 3127.3306 & 44.63353 & 8.201 \\
CID454 & 2824.2693 & 43.34466 & 8.100 & ... & ... & ... \\
CID50 & 2339.9104 & 43.93786 & 8.263 & 1938.5676 & 45.32766 & 8.145 \\
CID543 & 2188.8447 & 43.57404 & 8.005 & ... & ... & ... \\
CID597 & 1656.3296 & 43.32955 & 7.629 & ... & ... & ... \\
CID607 & 3009.1816 & 43.67079 & 8.335 & 4241.526 & 44.78209 & 8.542 \\
CID70 & 2480.4058 & 43.50531 & 8.076 & 3981.8574 & 45.1582 & 8.682 \\
LID1273 & 3223.8484 & 43.61001 & 8.361 & ... & ... & ... \\
LID1538 & 2941.422 & 43.59594 & 8.274 & ... & ... & ... \\
LID360 & 2481.7253 & 43.88091 & 8.283 & 2868.8992 & 45.08676 & 8.36 \\
XID2138 & 3185.8613 & 43.6148 & 8.354 & 2944.7766 & 44.80782 & 8.239 \\
XID2202 & 2973.2378 & 43.56249 & 8.265 & ... & ... & ... \\
XID2396 & 2271.2617 & 44.06196 & 8.306 & 2657.8386 & 45.50467 & 8.51 \\
CDFS-1 & ... & ... & ... & ... & ... & ... \\
CDFS-229 & ... & ... & ... & ... & ... & ... \\
CDFS-321 & 2441.93 & 43.92714 & 8.294 & ... & ... & ... \\
CDFS-724 & ... & ... & ... & ... & ... & ... \\
ECDFS-358 & 2237.2314 & 43.39674 & 7.927 & ... & ... & ... \\
SXDS-X1136 & 2759.8953 & 43.43305 & 8.129 & 6761.222 & 44.71429 & 8.912 \\
SXDS-X50 & 1816.672 & 43.42100 & 7.759 & ... & ... & ... \\
SXDS-X717 & 2930.7417 & 43.04988 & 7.970 & ... & ... & ... \\
SXDS-X735 & 2702.0962 & 43.69804 & 8.256 & 3519.6052 & 45.07463 & 8.532 \\
SXDS-X763 & 2961.1743 & 43.57321 & 8.267 & 4508.5146 & 44.51285 & 8.456 \\
SXDS-X969 & 2296.0566 & 43.50066 & 8.006 & 1695.7146 & 45.05337 & 7.886 \\
\enddata
\label{tab:result_mbh}
\tablecomments{
Column 1: Object ID.
Column 2: .
Column 3: HST filter. The samples with marker $^*$ have the ACS/F814W.
}
\end{deluxetable*}

\begin{figure*}
\centering
%\hspace{-5.5em}
{
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID1174_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID206_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID216_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID237_SB_profile.pdf}
\caption{\label{fig:QSO_decomp} 
\textcolor{red}{need to be written:}
%WFC3 images for 12 objects. In each row, observed data (first column), best-fit models (second column), and residuals (third column) are presented with the object name. All images are $10.8\arcsec\times10.8\arcsec$ in size and  displayed with an inverted asinh stretch. The fourth column shows the corresponding one-dimensional surface brightness profiles. In each top panel, the profiles measured from the data (open circles), the best-fit model (black solid line), and the sub-components of the model for bulge (blue solid line), disk (green solid line), AGN (red solid line) are shown. Residuals (gray circles), the difference of the profiles between the data and the best-fit model, are presented in each bottom panel. Note that the one-dimensional surface brightness profiles are shown for illustration purposes only, the actual fitting made use of the full two-dimensional images.
}}
\end{figure*}

>>>>

Our final sample is composed of 36  AGNs; 32 of them are new observations by HST/WFC3 \textcolor{red}{\bf (32+4?, the information of these four sample?)}. Table~\ref{tab:objlist} list all the AGN systems analyzed in this work.

To compare with the samples in the literature, we adopt the samples from ... \textcolor{blue}{\bf (H0licow7)}.
For the calibration with the local relation, we introduce the well-defined 19 local AGN measurements \citep{Ben++10, Peterson2004} which defines the zero-point.

@@

Having defined the recipes, we estimate the \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}. 14 of the overall systems have both \halpha\ and \hbeta\ emission line information; we adopt the average \mbh\ value by these two lines. We summarized the inference of the \mbh\ together with the details on the emission line in Table~\ref{tab:result_mbh}.

@@

\section{discuss}
\label{sec:dis}
\subsection{Systematic error}
\subsection{Fitting mask for CID206 and ECDFS-358}

@@

\begin{deluxetable*}{ccccccc}
\tablecolumns{7}
\tablewidth{0pt}
\tablecaption{Details of the weighting CID1174's inference. } 
\tablehead{ 
\colhead{PSF rank} &
\colhead{total $\chi ^2$} & 
\colhead{weights $w_i$} &
\colhead{host flux (counts)} &
\colhead{host flux ratio}&
\colhead{\Reff (arcsec)}&
\colhead{\sersic\ $n$}
 \\ 
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)} &
\colhead{(6)} &
\colhead{(7)} 
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
1 & 8646.711 & 1.000 & 99.102 & 41.9\% & 0\farcs{}298 & 1.932 \\
2 & 8816.947 & 0.849 & 76.740 & 33.0\% & 0\farcs{}365 & 1.102 \\
3 & 9304.841 & 0.530 & 128.618 & 54.7\% & 0\farcs{}231 & 2.780 \\
4 & 9652.575 & 0.379 & 187.498 & 79.0\% & 0\farcs{}116 & 6.175 \\
5 & 10018.324 & 0.267 & 75.061 & 32.3\%& 0\farcs{}365 & 1.226 \\
6 & 10087.456 & 0.249 & 79.835 & 34.3\% & 0\farcs{}358 & 1.195 \\
7 & 10457.811 & 0.174 & 108.580 & 46.4\% & 0\farcs{}262 & 2.190 \\
8 & 10721.421 & 0.135 & 63.994 & 27.8\% & 0\farcs{}406 & 0.720 \\
\hline\\
Weighted value & & & 103.534 $\pm$ 34.267 & 44.0\%$\pm$14.2\%& 0\farcs{}296$\pm$0\farcs{}079 & 2.173$\pm$1.500  \\
\enddata
\label{tab:weight_CID1174}
\tablecomments{
Column~1: The rank of the PSF from the library.
Column~2: Total $\chi ^2$ for the corresponding PSF.
Column~3: Weights for co-adding the inference.
Column~4-7: Fitted value for the host flux, host/total flux ratio, effective radius, and \sersic\ index.
For this sample, the inflation value $\alpha$ calculated by Eq.~\ref{eq:alpha} is 16.671.
}
\end{deluxetable*}

@@

\begin{deluxetable*}
{@{\extracolsep{4pt}}lcccccc}   % need for the gap between the clines.
\tablecolumns{7}
\tablewidth{0pt}
\tablecaption{The inference of the \mbh\ for the 32 systems.} 
\tablehead
{ 
\colhead{Target ID}&
  \multicolumn{3}{c}{using emission line \halpha}&
  \multicolumn{3}{c}{using emission line \hbeta} \\
  \cline{2-4}  \cline{5-7} \\
\colhead{}& 
\colhead{FWHM}& \colhead{$\log(\lambda \rm L _{H\alpha}$)}& \colhead{\mbh}&
\colhead{FWHM(5100)}& \colhead{$\log(\lambda \rm L _{\lambda5100})$}& \colhead{\mbh}\\
\colhead{}& 
\colhead{(\kms)}& \colhead{(${\rm erg~s^{-1}}$)}& 
\colhead{(M$_{\odot}$)}& \colhead{(\kms)}& 
\colhead{(${\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)}\\
\colhead{(1)}& 
\colhead{(2)}& \colhead{(3)}& 
\colhead{(4)}& \colhead{(5)}& 
\colhead{(6)}&\colhead{(7)}
}
\startdata 
CID1174 & 1906.3037 & 43.43237 & 7.992 & 5898.264 & 44.76243 & 8.833 \\
CID1281 & 1619.4891 & 43.23945 & 7.749 & ... & ... & ... \\
CID206 & 3333.5527 & 43.4776 & 8.528 & ... & ... & ... \\
CID216 & 2229.5232 & 42.84509 & 7.854 & ... & ... & ... \\
CID237 & 2112.3306 & 43.85546 & 8.289 & ... & ... & ... \\
CID255 & 1932.0933 & 43.9924 & 8.273 & 3709.241 & 45.37122 & 8.734 \\
CID3242 & 2543.2202 & 43.83323 & 8.449 & 3774.503 & 45.09891 & 8.613 \\
CID3570 & 1958.8551 & 43.16374 & 7.888 & ... & ... & ... \\
CID452 & 3457.8801 & 42.92298 & 8.295 & 3127.3306 & 44.63353 & 8.217 \\
CID454 & 2824.2693 & 43.34466 & 8.311 & ... & ... & ... \\
CID50 & 2339.9104 & 43.93786 & 8.423 & 1938.5676 & 45.32766 & 8.149 \\
CID543 & 2188.8447 & 43.57404 & 8.187 & ... & ... & ... \\
CID597 & 1656.3296 & 43.32955 & 7.813 & ... & ... & ... \\
CID607 & 3009.1816 & 43.67079 & 8.526 & 4241.526 & 44.78209 & 8.556 \\
CID70 & 2480.4058 & 43.50531 & 8.269 & 3981.8574 & 45.1582 & 8.689 \\
LID1273 & 3223.8484 & 43.61001 & 8.561 & ... & ... & ... \\
LID1538 & 2941.422 & 43.59594 & 8.469 & ... & ... & ... \\
LID360 & 2481.7253 & 43.88091 & 8.45 & 2868.8992 & 45.08676 & 8.369 \\
XID2138 & 3185.8613 & 43.6148 & 8.552 & 2944.7766 & 44.80782 & 8.252 \\
XID2202 & 2973.2378 & 43.56249 & 8.463 & ... & ... & ... \\
XID2396 & 2271.2617 & 44.06196 & 8.455 & 2657.8386 & 45.50467 & 8.511 \\
CDFS-1 & ... & ... & ... & ... & ... & ... \\
CDFS-229 & ... & ... & ... & ... & ... & ... \\
CDFS-321 & 2441.93 & 43.92714 & 8.457 & ... & ... & ... \\
CDFS-724 & ... & ... & ... & ... & ... & ... \\
ECDFS-358 & 2237.2314 & 43.39674 & 8.122 & ... & ... & ... \\
SXDS-X1136 & 2759.8953 & 43.43305 & 8.333 & 6761.222 & 44.71429 & 8.927 \\
SXDS-X50 & 1816.672 & 43.421 & 7.942 & ... & ... & ... \\
SXDS-X717 & 2930.7417 & 43.04988 & 8.204 & ... & ... & ... \\
SXDS-X735 & 2702.0962 & 43.69804 & 8.44 & 3519.6052 & 45.07463 & 8.54 \\
SXDS-X763 & 2961.1743 & 43.57321 & 8.465 & 4508.5146 & 44.51285 & 8.474 \\
SXDS-X969 & 2296.0566 & 43.50066 & 8.196 & 1695.7146 & 45.05337 & 7.895 \\
\enddata
\label{tab:result_mbh}
\tablecomments{
Column 1: Object ID.
Column 2-4: The emission line width (FWHM), continuum luminosity and inferred \mbh by \halpha\ emission line. 
Column 5-7: The inference by \hbeta\ emission line. 
}
\end{deluxetable*}

\begin{figure*}
\centering
%\hspace{-5.5em}
{
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID1174_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID206_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID216_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID237_SB_profile.pdf}
\caption{\label{fig:QSO_decomp} 
\textcolor{red}{need to be written:}
Figure illustrates the inference by WFC3 images for the 34 objects.
In each row, observed data (first column), best-fit models (second column), data subtracted by the inferred point source (third column),  normalized residuals (fourth column) are presented together with the target ID. In the fifth column, we present the 1-D surface brightness profiles and the corresponding residual. \textcolor{blue}{The different colors means blash blash...}
%In each row, observed data (first column), best-fit models (second column), and residuals (third column) are presented with the object name. All images are $10.8\arcsec\times10.8\arcsec$ in size and  displayed with an inverted asinh stretch. The fourth column shows the corresponding one-dimensional surface brightness profiles. In each top panel, the profiles measured from the data (open circles), the best-fit model (black solid line), and the sub-components of the model for bulge (blue solid line), disk (green solid line), AGN (red solid line) are shown. Residuals (gray circles), the difference of the profiles between the data and the best-fit model, are presented in each bottom panel. Note that the one-dimensional surface brightness profiles are shown for illustration purposes only, the actual fitting made use of the full two-dimensional images.
}}
\end{figure*}
